Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing

### 2020-02-06 Dissonance_Santiago_v1/Dissonance_Santiago_v1.tex
Reorganized folder structure and created a new version to revise the paper after receiving reviewer comments from Journal of Transportation and Health.

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \begin{abstract}
  Subjective wellbeing is a topic that has attracted considerable
  attention in recent years due to the way it correlates with health. From
  a transportation perspective, there is a burgeoning literature on the
  way travel can impact subjective wellbeing, and how this, in turn, can
  influence behavior. After decades of fascination with the automobile,
  subjective wellbeing is increasingly recognized as an alternative
  approach to assess transportation, and to gain valuable insights to
  attract and retain active travelers and users of public transportation.
  The objective of this paper is to analyze a number of affective values
  associated with subjective wellbeing and the modes of transportation
  that people commonly use. In particular, we are interested in the
  potential for dissonance with respect to the primary mode of travel. The
  study is based on data collected from a sample of travellers in the city
  of Santiago, in Chile. Participants in the study were asked about their
  usual mode of travel, and then were asked to name the mode or modes that
  they associate with the affective values of freedom, enjoyment,
  happiness, poverty, luxury and status. The results indicate that users
  of public transportation experience the most dissonance in terms of
  affective values, and active travellers the least. For those travellers
  who experience dissonance, active travel is the mode most commonly
  associated with freedom, enjoyment, and happiness, public transportation
  is most commonly associated with poverty, and the automobil is most
  commonly associated with luxury and status.
  \end{abstract}

@@

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

@@

\hypertarget{background}{%
\section{2. Background}\label{background}}

@@

\hypertarget{case-study-and-data}{%
\section{3. Case Study and Data}\label{case-study-and-data}}

\hypertarget{context}{%
\subsection{3.1 Context}\label{context}}

@@

\hypertarget{sample}{%
\subsection{3.2 Sample}\label{sample}}

@@

\hypertarget{analysis-and-results}{%
\section{4. Analysis and Results}\label{analysis-and-results}}

@@

\hypertarget{who-experiences-dissonance}{%
\subsection{4.1 Who experiences
dissonance?}\label{who-experiences-dissonance}}

To investigate the first question in our analysis, we create contingency
tables that tabulate the frequency of dissonance with respect to each
affective value, stratified by the attributes of Age, Education, Income,
Primary Mode of Travel, and typical Commute Time. Table
\ref{tab:cross-tabulation-results-without-instrumental} presents the
frequency (in percentage) of dissonance, in other words, the percentage
of respondents out of the total in their stratum who indicated mode or
mode(s) for the affective value that do not correspond to their primary
mode of travel.

@@

\hypertarget{age}{%
\subsubsection{4.1.1 Age}\label{age}}

@@

\hypertarget{education}{%
\subsubsection{4.1.2 Education}\label{education}}

@@

\hypertarget{income}{%
\subsubsection{4.1.3 Income}\label{income}}

@@

\hypertarget{primary-mode-of-travel}{%
\subsubsection{4.1.4 Primary mode of
travel}\label{primary-mode-of-travel}}

The variable that shows the largest differences in the frequency of
dissonance is the primary mode of travel. It can be seen in Table
\ref{tab:cross-tabulation-results-without-instrumental} that the
differences are significative for all six affective values. Dissonance
is particularly accute for users of public transportation when it comes
to the values of Freedom, Enjoyment, and Happiness: almost 100\% of
users of public transportation have identified other mode or modes as
better representing those values. Dissonance on these values is the
least for active travellers: less than 50\% of respondents associate
Freedom to a different mode, and only around 60\% identified a different
mode when responding to the values of Enjoyment and Happiness, compared
to approximately 79\% and 71\% of those who travelled by Car. The
picture changes when the values of Poverty, Luxury, and Status are
considered. In this case, dissonance is less frequent for people who
travel by car: less than 3\% of car users associate car with feelings of
poverty, 41\% associate Luxury with a mode other than car, and only
about 31\% relate Status to a different mode. Dissonance is more
frequent in these values for active travellers, and users of public
transportation and other modes, in no case being less than 75\%, and
being virtually 100\% for users of public transportation, who
consistently associate Luxury and Status with modes \emph{other} than
public transportation.

\hypertarget{typical-commute-time}{%
\subsubsection{4.1.5 Typical commute time}\label{typical-commute-time}}

@@

\hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
\subsection{4.2 Which modes do travellers associate with affective
values?}\label{which-modes-do-travellers-associate-with-affective-values}}

@@

\hypertarget{age-1}{%
\subsubsection{4.2.1 Age}\label{age-1}}

@@

\hypertarget{education-1}{%
\subsubsection{4.2.2 Education}\label{education-1}}

@@

\hypertarget{income-1}{%
\subsubsection{4.2.3 Income}\label{income-1}}

@@

\hypertarget{typical-commute-time-1}{%
\subsubsection{4.3.4 Typical commute
time}\label{typical-commute-time-1}}

@@

\hypertarget{conclusions}{%
\section{5. Conclusions}\label{conclusions}}

>>>>

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)
% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \begin{abstract}
  \textbf{Introduction}\\
  Subjective wellbeing is a topic that has attracted considerable
  attention in recent years due to the way it correlates with health. From
  a transportation perspective, there is a burgeoning literature on the
  way travel can impact subjective wellbeing, and how this, in turn, can
  influence behavior.\\
  \textbf{Objective}\\
  The objective of this paper is to analyze a number of affective values
  associated with subjective wellbeing and the modes of transportation
  that people commonly use. In particular, we are interested in the
  potential for dissonance with respect to the primary mode of travel.\\
  \textbf{Materials and Methods}\\
  The study is based on data collected from a sample of travellers in the
  city of Santiago, in Chile. Participants in the study were asked about
  their usual mode of travel, and then were asked to name the mode or
  modes that they associate with the affective values of freedom,
  enjoyment, happiness, poverty, luxury and status. Analysis is based on
  tests of independence and visualization via mosaic plots.\\
  \textbf{Results}\\
  The results indicate that users of public transportation experience the
  most dissonance in terms of affective values, and active travellers the
  least. For those travellers who experience dissonance, active travel is
  the mode most commonly associated with freedom, enjoyment, and
  happiness, public transportation is most commonly associated with
  poverty, and the automobil is most commonly associated with luxury and
  status.
  \end{abstract}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{background}{%
\section{Background}\label{background}}

@@

\hypertarget{case-study-and-data}{%
\section{Case Study and Data}\label{case-study-and-data}}

\hypertarget{context}{%
\subsection{Context}\label{context}}

@@

\hypertarget{sample}{%
\subsection{Sample}\label{sample}}

@@

\hypertarget{analysis-and-results}{%
\section{Analysis and Results}\label{analysis-and-results}}

@@

\hypertarget{who-experiences-dissonance}{%
\subsection{Who experiences
dissonance?}\label{who-experiences-dissonance}}

To investigate the first question in our analysis, we create contingency
tables that tabulate the frequency of dissonance with respect to each
affective value, stratified by the attributes of Age, Education, Income,
Primary Mode of Travel, and typical Commute Time. Table
\ref{tab:cross-tabulation-results} presents the frequency (in
percentage) of dissonance, in other words, the percentage of respondents
out of the total in their stratum who indicated mode or mode(s) for the
affective value that do not correspond to their primary mode of travel.

@@

\hypertarget{age}{%
\subsubsection{Age}\label{age}}

@@

\hypertarget{education}{%
\subsubsection{Education}\label{education}}

@@

\hypertarget{income}{%
\subsubsection{Income}\label{income}}

@@

\hypertarget{primary-mode-of-travel}{%
\subsubsection{Primary mode of travel}\label{primary-mode-of-travel}}

The variable that shows the largest differences in the frequency of
dissonance is the primary mode of travel. It can be seen in Table
\ref{tab:cross-tabulation-results} that the differences are
significative for all six affective values. Dissonance is particularly
accute for users of public transportation when it comes to the values of
Freedom, Enjoyment, and Happiness: almost 100\% of users of public
transportation have identified other mode or modes as better
representing those values. Dissonance on these values is the least for
active travellers: less than 50\% of respondents associate Freedom to a
different mode, and only around 60\% identified a different mode when
responding to the values of Enjoyment and Happiness, compared to
approximately 79\% and 71\% of those who travelled by Car. The picture
changes when the values of Poverty, Luxury, and Status are considered.
In this case, dissonance is less frequent for people who travel by car:
less than 3\% of car users associate car with feelings of poverty, 41\%
associate Luxury with a mode other than car, and only about 31\% relate
Status to a different mode. Dissonance is more frequent in these values
for active travellers, and users of public transportation and other
modes, in no case being less than 75\%, and being virtually 100\% for
users of public transportation, who consistently associate Luxury and
Status with modes \emph{other} than public transportation.

\hypertarget{typical-commute-time}{%
\subsubsection{Typical commute time}\label{typical-commute-time}}

@@

\hypertarget{which-modes-do-travellers-associate-with-affective-values}{%
\subsection{Which modes do travellers associate with affective
values?}\label{which-modes-do-travellers-associate-with-affective-values}}

@@

\hypertarget{age-1}{%
\subsubsection{Age}\label{age-1}}

@@

\hypertarget{education-1}{%
\subsubsection{Education}\label{education-1}}

@@

\hypertarget{income-1}{%
\subsubsection{Income}\label{income-1}}

@@

\hypertarget{typical-commute-time-1}{%
\subsubsection{Typical commute time}\label{typical-commute-time-1}}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}
